Spatial Reasoning and Statistical Graphics

### 2014-10-16 Paper/Draft1/TestingVisualAptitude.Rnw
Grammar fix.

\section{Results}
Results are based on an evaluation of \Sexpr{nrow(ans)} undergraduate students at Iowa State University. 
Scoring of all test results was done such that random guessing leads to an expected value of 0; therefore each question answered correctly contributes to the score by 1, while a wrong answer is scored by $-1/(k-1)$, where $k$ is the total number of possible answers to the question. Thus, for a test consisting of multiple choice questions with $k$ suggested answers with a single correct answer each, the score is calculated as
\begin{eqnarray}\label{eq.scoring}
\# \text{correct answers } - 1/(k-1) \cdot \# \text{wrong answers}.
\end{eqnarray}
This allows us to compare each participant's score in light of how many problems were attempted as well as the number of correct responses. Combining accuracy and speed into a single number does not only make a comparison of test scores easier,  this scoring mechanism is also used on many standardized tests, such as the SAT and the battery of psychological tests \citep{diamond1973correction, ekstrom1976manual} which parts of this test are drawn from.

>>>>

\section{Results}
Results are based on an evaluation of \Sexpr{nrow(ans)} undergraduate students at Iowa State University. 
Scoring of all test results was done such that random guessing leads to an expected value of 0; therefore each question answered correctly contributes to the score by 1, while a wrong answer is scored by $-1/(k-1)$, where $k$ is the total number of possible answers to the question. Thus, for a test consisting of multiple choice questions with $k$ suggested answers with a single correct answer each, the score is calculated as
\begin{eqnarray}\label{eq.scoring}
\# \text{correct answers } - 1/(k-1) \cdot \# \text{wrong answers}.
\end{eqnarray}
This allows us to compare each participant's score in light of how many problems were attempted as well as the number of correct responses. Combining accuracy and speed into a single number does not only make a comparison of test scores easier,  this scoring mechanism is also used on many standardized tests, such as the SAT and the battery of psychological tests \citep{diamond1973correction, ekstrom1976manual} from which parts of this test are drawn.
